---
title: "Replication Project"
author: "Xavier Adomatis"
date: '2022-05-02'
output:
  html_document: default
  pdf_document: default
---

```{r}
# Load necessary packages
library(haven)
library(dplyr)
library(fastDummies)
library(miceadds)
library(purrr)
library(openxlsx)
# Read in data
df <- read_dta("master.dta")
```
# Variable Prep
```{r}
# Get year dummies, as the stata naming for these variables is incompatible with R
df <- dummy_cols(df, select_columns = 'year') #,remove_first_dummy = TRUE
```

# Recreation of Table 2

## Build a function to determine the output of the result combinations
```{r}
# Initiate a function with no additional covariates
reg_func <- function(miles,panel,parity) {
  # Limit the dataframe to only include those within a specified distance
  df_lim <- df[abs(df$y) < miles,]
  
  # For Panel A results, ensure that variables reference all mortgages
  if(panel=="A") {var <- df_lim$d90plus_lpsquery; fico <- df_lim$fico_orig; n_loans <- df_lim$Nloans_lpsquery; Mortgages <- "All"}
  
  # For Panel B results, ensure that results are limited to nonprime mortgage metrics
  if(panel=="B") {var <- df_lim$d90plus_absquery; fico <- df_lim$fico_orig_absquery; n_loans <- df_lim$Nloans_absquery; Mortgages <- "Nonprime"}
  
  # For odd numbered regressions include only year effects
  if(parity=="odd") {reg <- lm.cluster(var ~ texas + y 
                                       + year_2008 + year_2009 + year_2010 + year_2011, 
                                       data = df_lim, weights=(n_loans), 
                                       cluster = 'countyfips'); Covariates <- "Only Year Effects"}
  
  # For even numbered regressions include additional covariates
  if(parity=="even") {reg <- lm.cluster(var ~ texas + y 
                                        + ur + impL1D1lnhpi + fico 
                                        + year_2008 + year_2009 + year_2010 + year_2011, 
                                        data = df_lim, weights=(n_loans), 
                                        cluster = 'countyfips'); Covariates <- "Covariates"}
  
  # Ensure ouputs are captured for each regression
  Texas <- round(summary(reg)[2,1],3)
  SE <- round(summary(reg)[2,2],3)
  N_Observations <- length(df_lim$countyfips)
  N_Counties <- length(unique(df_lim$countyfips))
  R_sqd <- round(summary(reg$lm_res)$r.squared,3)
  
  # Ensure identifying info is included with the output
  Miles_from_Border <- miles
  
  # Build a dataframe row (include r when solved)
  coef_se <- data.frame(Texas,SE,N_Observations,N_Counties,R_sqd,Miles_from_Border,Covariates,Mortgages)
  
  # Return a dataframe row containing the relevant information
  return(coef_se)
}
```

### Run as a test
Results should yield an estimate of -2.594 and an SE of 1.567 for Regression 1.A, and they do.
```{r}
# Test run
reg_func(25,"A","odd")
```
## Create the results table

### Build a dataframe of input combinations
```{r}
# Set list of possible distances
distances <- rep(c(25,50,75,100,1000),each=2,times=2)
# Set list of Panel names
panels <- rep(c("A","B"),each=10)
# Alternate even and odd regressions
parities <- rep(c("odd","even"),times=10)
# Merge into a data frame of all possible input combinations
inputs <- data.frame(distances,panels,parities)
```

### Construct a table of results
```{r}
# Apply the function to row 1 to begin our output table
appended <- reg_func(inputs$distances[1],inputs$panels[1],inputs$parities[1])
# Remove the already-processed row from the sample
inputs <- inputs %>% slice(-1)
# Iterate over the inputs dataframe to create the results output
for (i in 1:19){
appended[i+1,] <- reg_func(inputs$distances[i],inputs$panels[i],inputs$parities[i])
}
```

### Organize the data into table format
```{r}
# Repair NAs caused by defualt settings
appended$Covariates <- as.character(appended$Covariates)
appended$Covariates[is.na(appended$Covariates)] <- "Covariates"
appended$Mortgages <- as.character(appended$Mortgages)
appended$Mortgages[is.na(appended$Mortgages)] <- "Nonprime"

# Change column orders to match the tables
appended <- appended %>%
  select(Miles_from_Border, Covariates, Mortgages, everything())

# Produce the panels by transposing the data
Panel_A <- data.frame(t(appended[appended$Mortgages == "All",]))
Panel_B <- data.frame(t(appended[appended$Mortgages != "All",]))

# Write to Excel for easy pasting
write.xlsx(Panel_A, "T2_Panel_A.xlsx")
write.xlsx(Panel_B, "T2_Panel_B.xlsx")
```

# Recreation of Figure 3

## Build a function to output the appropriate plots
```{r}
plotter <- function(title,miles) {
  # Limit the dataset to the preset distance
  df_lim <- df %>% filter(abs(y) < miles)
  # Aggregate means
  agg_def <- aggregate(df_lim$d90plus_absquery, list(df_lim$y), FUN=mean)
  # Create color variants for both sides fo the border
  agg_def$Texas <- ifelse(agg_def$Group.1 < 0, "darkslategray2", "firebrick3")
  # Split the data for abline purposes
  neg = df_lim[df_lim$y > 0, ]
  pos = df_lim[df_lim$y < 0, ]
  
  # Create primary scatterplot
  plot(agg_def$Group.1, agg_def$x, type = "p", col = agg_def$Texas, pch = 16, xlab = "Distance from Border", ylab = "Mortgage Defaulr Rate", main = title)
  # Add threshold line
  abline(v=0, col="gray", lty = 2, lwd = 2)
  # Cut regression lines above and below the thresholds
  clip(0, 100, 5, 25)
  abline(lm.cluster(d90plus_absquery ~ y, data = neg, weights=(neg$Nloans_abss), cluster = 'countyfips'), col = "firebrick3", lwd = 5)
  grid(nx = NA,ny = NULL,lty = 2, col = "gray", lwd = 2)
  clip(-100, 0, 5, 25)
  abline(lm.cluster(d90plus_absquery ~ y, data = pos, weights=(pos$Nloans_abss), cluster = 'countyfips'), col = "darkslategray2", lwd = 5)
  grid(nx = NA,ny = NULL,lty = 2, col = "gray", lwd = 2)
}
```

## Produce the resulting plots
```{r}
#Produce plots
plotter("Panel A. Within 25 Miles",25)
plotter("Panel B. Within 50 Miles",50)
plotter("Panel C. Within 75 Miles",75)
plotter("Panel D. Within 100 Miles",100)
```


# Additions to the paper

## Conduct a permutation test
```{r}
# Set baseline regression to see the resulting coefficients and assess significance
ptest.lm = lm(d90plus_absquery ~ texas, data = df, weights=df$Nloans_abss)
summary(ptest.lm)

# Preset repretitions at 500
reps = 500

# Create matrix to hold results
cm = matrix(NA, reps, 1)

# Rerun the regression while randomizing the treatment variable
for(ii in 1:reps) {
  # Randomize whether or not the observation is in Texas
  df$texas = sample(c(0,1), dim(df)[1], replace = TRUE) 
  # Set the Regression
  ptest.lm = lm(d90plus_absquery ~ texas + y + ur + impL1D1lnhpi + fico_orig_absquery + year_2008 + year_2009 + year_2010 + year_2011, data = df, weights=df$Nloans_abss) 
  # Record results
  cm[ii,1]=coefficients(ptest.lm)[2]
}
# Plot
hist(cm[,1],breaks=20,main="Permutation Test",xlab="Permutation Estimate")
abline(v=0, col="black")
```

## Test the permutation test across all possible bandwidths
```{r}
# Preset repetitions at 100 to preserve computing power
reps = 100
# Enumerate bandwidths
bwidths = seq(from=0, to=400, by=5)
# Set a matrix all possible distance bounds
CoefMatrix  = matrix(NA, length(bwidths), 5)

# Conduct the permutation test across all bandwidths
for(ii in 1:length(bwidths)) {
  dta <- df[abs(df$y) < bwidths[ii],]
  # Create matrix to hold results
  cm = matrix(NA, reps, 1)
  # Rerun the regression while randomizing the treatment variable
  for(v in 1:reps) {
    # Randomize whether or not the observation is in Texas
    df$texas = sample(c(0,1), dim(df)[1], replace = TRUE)
    # Set the Regression
    ptest.lm = lm(d90plus_absquery ~ texas+ y + ur + impL1D1lnhpi + fico_orig_absquery + year_2008 + year_2009 + year_2010 + year_2011, data = df, weights=df$Nloans_abss)
    # Record results
    cm[v,1]=coefficients(ptest.lm)[2]
  }
  # Load the aggregate results of each permutation into a larger matrix
  # Record basic outputs from each result
  CoefMatrix[ii,1]=bwidths[ii]
  CoefMatrix[ii,2]= median(cm)
  CoefMatrix[ii,3]= sd(cm)
  # Set bounds at 95% confidence levels
  CoefMatrix[ii,4]= CoefMatrix[ii,2] - 2*CoefMatrix[ii,3]
  CoefMatrix[ii,5]= CoefMatrix[ii,2] + 2*CoefMatrix[ii,3]
}

# Plot
plot(
  CoefMatrix[,1],
  CoefMatrix[,2],
  type="b",
  col="blue",
  xlab="Bandwidth",
  ylab="Estimate with Randomized Independent Variable",
  main="Permutation Variance by Bandwidth",ylim=c(-2,2))

lines(CoefMatrix[,1],CoefMatrix[,4],type="l",col="red")
lines(CoefMatrix[,1],CoefMatrix[,5],type="l",col="red")

abline(h=0)

```
